---
title: "Marriage"
subtitle: None
author: 
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/YichengFu/week3_activity."
date: 19 September 2024
date-format: long
abstract: "This paper focuses on people's finance and its impact on marriage using data from opendatatoronto. This paper uses the data to explorre the impact of marriage on individuals financial status like income employment and etc. The author utilized regression models to look into the patterns. The results show that marriage often leads to higher employment or financial situation such as higher income."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))

```


# Introduction


# Data {#sec-mydatasection}

from @opendatatorotno.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false



ggplot(data = data, aes(x = year, y = marriage_licenses)) +
  geom_bar(stat = "identity") + labs(title = "Number of Marriage per Year from 2011 to 2024",x = "Year", y = "Number of Marriage")

```

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


