---
title: "Marriage"
subtitle: None
author: 
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/YichengFu/week3_activity."
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))

```


# Introduction


# Data {#sec-mydatasection}

from @opendatatorotno.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false



ggplot(data = data, aes(x = year, y = marriage_licenses)) +
  geom_bar(stat = "identity") + labs(title = "Number of Marriage per Year from 2011 to 2024",x = "Year", y = "Number of Marriage")

```

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


